\section{Legal Disclaimer}
\textbf{BEFORE DOWNLOADING, PRINTING OR VIEWING LITEPAPER AND/OR ANCILLARY INFORMATION CONTAINED HEREIN, PLEASE CAREFULLY READ THIS DISCLAIMER. BY ACCESSING THE INFORMATION, YOU AGREE TO AND ACKNOWLEDGE THAT YOU HAVE READ AND ACCEPT THESE TERMS AND CONDITIONS OF ACCESS. IF YOU DO NOT UNDERSTAND THE INFORMATION CONTAINED IN THIS LITEPAPER, YOU SHOULD CONSULT YOUR PROFESSIONAL ADVISER WITHOUT DELAY.}

\subsection{Information purposes only}
This Litepaper is for general information purposes only and may be subject to change without prior notice. Astro Labs Research Ltd (“Astro Labs”) and any current or future affiliated entities, their managers, directors, officers, employees, advisors, consultants, agents, or any other person (the “Astro Team”) do not make or purport to make, and hereby disclaim, any representation, undertaking or warranty in any form whatsoever to any person or entity, including any representation, undertaking or warranty concerning the accuracy and completeness of any of the information set out in this Litepaper, which is issued by Astro Labs in good faith and is provided for reference purposes only. Nothing contained in this Litepaper is or may be relied upon as a promise, representation, or undertaking as to the future performance of the Astro Token. By continuing to use the information contained in this Litepaper, you agree to the exclusion by Astro Labs, to the extent permitted by applicable law and regulation, of any and all liability for any direct, indirect, punitive, consequential, incidental, special or other damages, including, without limitation, loss of profits, revenue or data arising out of or relating to your use of and our provision of this Litepaper.

Astro Labs does not guarantee the accuracy of any information and disclaims all representations and warranties, whether express or implied, to the extent permitted by applicable law and regulation. Further, circumstances may change, and this Litepaper may become outdated. Astro Labs is under no obligation to update or correct this Litepaper in connection therewith.

This Litepaper may be translated into a language other than English for information purposes only. In such case, the English language version shall always prevail over the translated versions of this Litepaper.

\subsection{No contractual relationship}
The information herein does not imply any elements of a contractual relationship nor form the basis of or be relied upon in connection with, any investment decision. The information set out in this Litepaper is not legally binding and is for community discussion only. It provides an initial overview of certain business and technical essentials underlying the Astro Protocol. It does not constitute advice or personal recommendation for which Astro Labs would owe a duty of suitability. If you are unsure about the meaning of any information provided in this Litepaper, please consult your financial or other professional adviser. Any offering or sale of Astro Tokens shall be governed by separate terms and conditions. In the event of a conflict between this Litepaper and the applicable terms and conditions, the terms and conditions shall prevail.

\subsection{Third-party information}
Astro Labs accepts no liability for damages, whether indirect or consequential, of any kind arising from the use, reference, or reliance on the contents of this Litepaper. This Litepaper may contain references to data, industry publications, and/or third-party research. No warranty is given to the accuracy and completeness of such third-party information. Neither the third-party information, its inferences nor its assumptions have been independently verified.

\subsection{No offer of securities}
This Litepaper does not constitute a prospectus, an offer of any sort including securities, a solicitation for investment in securities in any jurisdiction, or any offer to sell any product, item, or asset, whether digital or otherwise. No information in this Litepaper should be considered as business, legal, financial, or tax advice regarding the Astro Protocol or the Astro Token. Please consult your own legal, financial, tax, or another professional adviser regarding this project and the Astro Token. Astro Tokens do not in any way represent any shareholding, participation, right, title, or interest in any entity including Astro Labs or its affiliates, undertaking, or enterprise. Astro Tokens do not entitle anyone to any promise of dividends, revenue, fees, profits, or investment returns.

\subsection{Risk associated with the purchase of Astro Tokens}
Prospective purchasers of Astro Tokens should evaluate all risks and uncertainties associated with the purchase of Astro Tokens. This Litepaper does not constitute advice nor a recommendation by the Astro Team or Astro Labs on the merits of purchasing or holding Astro Tokens or any other token or cryptocurrency. Such purchase and holding carry substantial risks that could lead to a loss of part, or all, of the funds invested. As of the date hereof, the Astro Token has no known potential uses outside of the Astro Protocol. No promises of future performance, value, or utility are or will be made concerning the Astro Token, including no promise that the Astro Protocol will be launched and no guarantee that the Astro Tokens will have any intrinsic value. Astro Tokens are designed and intended for future use on public Astro Protocol, for governance to allow Astro Token holders to participate in key decision-making processes for protocol upgrades, risk management and other critical decisions. The Astro Team may decide to amend the intended functionality of Astro Tokens for any reason, including to ensure compliance with any legal or regulatory requirements to which it is subject, which may affect the utility or any other properties of the Astro Tokens. Any Astro Token could be impacted by regulatory action, including potential restrictions on the ownership, use, or possession of such tokens. Regulators or other competent authorities may demand that the mechanics of the Astro Tokens be altered, entirely or in part.