\documentclass{article}
\usepackage{amsmath}
\usepackage{hyperref}
\usepackage{graphicx}
\usepackage{fancyhdr}
\usepackage{titlesec}

\usepackage[normalem]{ulem}



\usepackage[margin=1in]{geometry} % Adjust the margin as needed



\title{\textbf{Astro: Over-collateralized stablecoin built on hyper parallel computer}\\Litepaper v1.0}


\author{
    By Astro Labs Research.\\
    In collaboration with Community Labs.\\[1em]
    Contributors: Kadar Abdi, Eric Crooks, Guilherme Lopes, Bithiah Koshy
}
\date{July 2024}

\begin{document}

\maketitle

\section*{Abstract}
Astro introduces USDA, an over-collateralized stablecoin developed on AO’s hyper parallel computing environment. This litepaper presents an overview of the protocol’s design - emphasizing stability, scalability, and security for digital currency transactions. It employs a robust collateralization mechanism to unlock and maintain liquidity while aiming to minimize volatility. The litepaper also briefly outlines the protocol’s governance model, and the economic incentives designed to foster a decentralized ecosystem. The content aims to offer a foundational understanding of Astro Protocol’s operational framework and security features, setting the stage for a comprehensive full whitepaper.

\section*{Motivation}
Over the past decade, blockchain technology has transformed financial services, once dominated by traditional intermediaries like banks and other institutions. Platforms like Ethereum have enabled the development of Decentralized Finance (DeFi), providing open, transparent financial tooling that have reduced operational costs and complexity for users globally.
Astro's introduction of the USDA stablecoin to the Arweave ecosystem is a major step forward. USDA aims to provide stability to the permaweb’s economic environment, leveraging Arweave's decentralized storage and the innovative aoComputer (AO) for smart contract-like \underline{processes}, enabling secure and efficient value exchange. The rapid growth of DeFi since 2020 underscores the need for stablecoins like USDA. Existing stablecoins like USDC and USDT, along with decentralized options like MakerDAO’s DAI, have enhanced transactional stability and fostered a low-volatility store of value within the Ethereum ecosystem. However, the absence of a stablecoin can hinder ecosystem development by restricting liquidity and value movement. USDA addresses these issues by supporting economic activities on AO and fostering the growth of its financial ecosystem. Astro’s USDA is designed to facilitate seamless transactions, enhance liquidity, and stabilize the Arweave ecosystem, encouraging broader adoption and innovation in DeFi applications.
\\
\\
\\
\\\\\\\\
\\
\tableofcontents
\newpage
\input{the_astro_protocol}
\input{risk_factors_and_mitigations}
\input{rest}
\input{legal}






\end{document}