\section{Governance of the Protocol}
Astro Protocol’s governance model will be designed to evolve from being initially stewarded to fully decentralized, mirroring successful frameworks like MakerDAO’s. Astro Labs will have a major role as a contributor, overseen by the Astro Foundation. The protocol's development will introduce the Astro Token (AST) for governance, with a clear roadmap towards decentralization.

Executive Voting and Governance Polling empower AST holders to participate in key decision-making processes for protocol upgrades, risk management, and other critical decisions. This approach strives for stability, transparency, and resilience in the Astro Protocol with an inclusive governance structure.

\section{Conclusion}
The Astro Protocol uses an innovative compute environment to introduce the USDA stablecoin, which is crafted to enhance liquidity and ensure stability across the ecosystem. The protocol's architecture prioritizes adaptability, considering potential changes in use-cases, community dynamics, and technology. Astro’s modular approach ensures continuous support for stable transactions, evolving with the ecosystem’s growth.

Astro brings two significant innovations to enhance the DeFi ecosystem:
\begin{itemize}
    \item \textbf{Stable Value Preservation}: USDA provides a stable value against volatile market conditions, aiding in financial planning and risk management for users across the network.
    \item \textbf{Enhanced Liquidity Solutions}: By integrating with the aoComputer (AO), Astro allows for efficient and secure smart contract executions, bolstering the liquidity and usability of USDA within various financial applications.
\end{itemize}

Following its deployment, Astro will continue to advance its commitment to decentralization with the introduction of additional features. A Governance Model will be implemented, allowing users to participate actively in the evolution of the protocol:
\begin{itemize}
    \item \textbf{Protocol Level}: An introduction of AST (Astro Token) for overarching updates and strategic decisions, enhancing user involvement and transparency.
    \item \textbf{Customizable Modules}: Enabling users to adapt and deploy tailored solutions based on Astro’s core smart contracts, fostering innovation and diversification within the ecosystem.
\end{itemize}

Through these measures, Astro aims to establish a resilient and adaptive framework that not only supports the growth of aoComputer (AO) but also sets a new standard for stability and user empowerment in the DeFi sector.

\section{Acknowledgements}
\begin{itemize}
    \item MakerDAO SAI Whitepaper. \url{https://makerdao.com/en/whitepaper/sai}
    \item MakerDAO DAI Whitepaper. \url{https://makerdao.com/pt-BR/whitepaper}
    \item Liquity Whitepaper. \url{https://docsend.com/view/mk99y5abnr8yqxws}
\end{itemize}